---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wildlandhydRo

<!-- badges: start -->
<!-- badges: end -->

The goal of wildlandhydRo is to create wrapper functions around commonly used packages like [streamstats](https://github.com/markwh/streamstats), [nhdplusTools](https://github.com/USGS-R/nhdplusTools), [snotelr](https://github.com/bluegreen-labs/snotelr),[dataRetrieval](https://github.com/USGS-R/dataRetrieval)  and [AOI](https://github.com/mikejohnson51/AOI) and provide accessible functions for culvert sizing, quick reports and EDA into extreme events. Mostly being able to batch (get more than one) in a more direct approach. Basically, a package for me but worth sharing with others.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joshualerickson/wildlandhydRo")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wildlandhydRo)
## basic example code
```

